USA

### 2020-12-01 src/uk.Rmd
responses

base <- lm(r_diff_tr ~ log(download2011) + log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share, data = data, subset = n.tests2011>20)
#nobs(base)

@@

# interactions
int_density <- lm(r_diff_tr ~ log(download2011)*pop.dens + log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share, data = data, subset = n.tests2011>20)
#nobs(int_density)

int_pop <- lm(r_diff_tr ~ log(download2011)*log(pop2011) + log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share, data = data, subset = n.tests2011>20)
#nobs(int_pop)

# 2 SLS with IV
model_iv1 <- ivreg(r_diff_tr ~ log(download2011) + log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share 
                   | log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share + uni.freq
                     , data = data, subset = n.tests2011>30)
#summary(model_iv1, vcov = sandwich, diagnostics = TRUE)
#nobs(base)

model_iv2 <- ivreg(r_diff_tr ~ log(download2011) + log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share 
                   | log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share + uni.freq + n.tests2011
                     , data = data, subset = n.tests2011>30)
#summary(model_iv2, vcov = sandwich, diagnostics = TRUE) #yes
```

@@

```{r}
# Table 9
data.for.decr <- data %>%
  dplyr::select(r_diff_tr, download2011, pop2011, n.tests2011,  
         unemployment.share, british.pop.share, pop.dens, 
         work.home.share, services.share, uni.freq) %>%
  mutate(n.tests2011perhab = n.tests2011/pop2011) %>%
  dplyr::select(-n.tests2011) %>%
  dplyr::select(r_diff_tr, download2011, pop2011, n.tests2011perhab,  # re-redring
         unemployment.share, british.pop.share, pop.dens, 
         work.home.share, services.share, uni.freq)

path.out <- paste(path, "/outputs/table9.htm", sep = "")

stargazer(as.data.frame(data.for.decr), out=path.out, type="html", summary = T,
          covariate.labels=c("normalized difference in ranks, 2011-14", "download speed, 2011", "population, 2011",  
                             "broadband tests per capita, 2011", "% of unemployment, 2011", "% of British population, 2011", 
                             "population density, 2011", "% of people working from home, 2011",
                             "employment in service, 2011 (%)", "Number of universities"))

@@

path.out <- paste(path, "/outputs/table10.htm", sep = "")

stargazer(base, int_density, int_pop, base_glm, type="html",
          se = list(rob.base[,"Std. Error"], rob.int_density[,"Std. Error"], rob.int_pop[,"Std. Error"], rob.base_glm[, "Std. Error"]), 
          dep.var.labels=c("Normalized difference in ranks, 2011-18"),
          #dep.var.caption = "Normalized difference in ranks, 2011-18",
          column.labels = c("OLS", "GLM"),
          column.separate = c(3,1),
          covariate.labels=c("download speed, 2011 (log)", "population, 2011 (log)",  
                             "broadband tests per capita, 2011", "% of unemployment, 2011", "% of British population, 2011", 
                             "population density, 2011", "% of people working from home, 2011",
                             "employment in service, 2011 (%)", "download speed, 2011 (log) x pop. density, 2011", 
                             "download speed, 2011 (log) x population, 2011 (log)"), 
          out=path.out, single.row = FALSE, df = FALSE, omit.stat = c("rsq", "f"), 
          notes = "Robust Std. Error parenthesis")

@@

path.out <- paste(path, "/outputs/table11.htm", sep = "")

stargazer(model_iv1, model_iv2, type = "html", 
          se = list(rob.model_iv1[,"Std. Error"], rob.model_iv2[,"Std. Error"]), 
          dep.var.labels=c("Normalized difference in ranks, 2011-18"),
          covariate.labels=c("download speed, 2011 (log)", "population, 2011 (log)",  
                             "broadband tests per capita, 2011", "% of unemployment, 2011", "% of British population, 2011", 
                             "population density, 2011", "% of people working from home, 2011",
                             "employment in service, 2011 (%)"),
          out=path.out, single.row = FALSE, df = FALSE, 
          omit.stat = c("rsq", "f"), notes = c("Robust Std. Error in parenthesis", "IVs: (1) Number of universities",
                                               "IVs: (2) Number of universities, Number of broadband tests, 2011"),
          add.lines = list(c(rownames(summ.fit1$diagnostics)[1],                    # use rownames as line name. in this case Weak insterumetns
                             round(summ.fit1$diagnostics[1, "statistic"], 2), 
                             round(summ.fit2$diagnostics[1, "statistic"], 2)), 
                           c(rownames(summ.fit1$diagnostics)[2], 
                             round(summ.fit1$diagnostics[2, "statistic"], 2), 
                             round(summ.fit2$diagnostics[2, "statistic"], 2)), 
                           c("P-value", 
                             round(summ.fit1$diagnostics[2, "p-value"], 2), 
                             round(summ.fit2$diagnostics[2, "p-value"], 2)), 
                           c(rownames(summ.fit1$diagnostics)[3], 
                             round(summ.fit1$diagnostics[3, "statistic"], 2), 
                             round(summ.fit2$diagnostics[3, "statistic"], 2)),
                           c("P-value", 
                             round(summ.fit1$diagnostics[3, "p-value"], 2), 
                             round(summ.fit2$diagnostics[3, "p-value"], 2))
          ))
```

>>>>

base <- lm(r_diff ~ log(download2011) + log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share, data = data, subset = n.tests2011>20)
#nobs(base)

@@

# interactions
int_density <- lm(r_diff ~ log(download2011)*pop.dens + log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share, data = data, subset = n.tests2011>20)
#nobs(int_density)

int_pop <- lm(r_diff ~ log(download2011)*log(pop2011) + log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share, data = data, subset = n.tests2011>20)
#nobs(int_pop)

# 2 SLS with IV
model_iv1 <- ivreg(r_diff ~ log(download2011) + log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share 
                   | log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share + uni.freq
                     , data = data, subset = n.tests2011>30)
#summary(model_iv1, vcov = sandwich, diagnostics = TRUE)
#nobs(base)

model_iv2 <- ivreg(r_diff ~ log(download2011) + log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share 
                   | log(pop2011) + I(n.tests2011/pop2011) + unemployment.share + 
                     british.pop.share +  pop.dens + work.home.share + services.share + uni.freq + n.tests2011
                     , data = data, subset = n.tests2011>30)
#summary(model_iv2, vcov = sandwich, diagnostics = TRUE) #yes
```

@@

```{r}
# Table 9
data.for.decr <- data %>%
  dplyr::select(r_diff, download2011, pop2011, n.tests2011,  
         unemployment.share, british.pop.share, pop.dens, 
         work.home.share, services.share, uni.freq) %>%
  mutate(n.tests2011perhab = n.tests2011/pop2011) %>%
  dplyr::select(-n.tests2011) %>%
  dplyr::select(r_diff, download2011, pop2011, n.tests2011perhab,  # re-redring
         unemployment.share, british.pop.share, pop.dens, 
         work.home.share, services.share, uni.freq)

#path.out <- paste(path, "/outputs/table9.htm", sep = "")

stargazer(as.data.frame(data.for.decr), 
          #out=path.out, 
          type="text", summary = T,
          covariate.labels=c("difference in ranks, 2011-14", "download speed, 2011", "population, 2011",  
                             "broadband tests per capita, 2011", "% of unemployment, 2011", "% of British population, 2011", 
                             "population density, 2011", "% of people working from home, 2011",
                             "employment in service, 2011 (%)", "Number of universities"))

@@

# path.out <- paste(path, "/outputs/table10.htm", sep = "")

stargazer(base, int_density, int_pop, base_glm, 
          type="text",
          se = list(rob.base[,"Std. Error"], rob.int_density[,"Std. Error"], rob.int_pop[,"Std. Error"], rob.base_glm[, "Std. Error"]), 
          dep.var.labels=c("Difference in ranks, 2011-18"),
          #dep.var.caption = "Normalized difference in ranks, 2011-18",
          column.labels = c("OLS", "GLM"),
          column.separate = c(3,1),
          covariate.labels=c("download speed, 2011 (log)", "population, 2011 (log)",  
                             "broadband tests per capita, 2011", "% of unemployment, 2011", "% of British population, 2011", 
                             "population density, 2011", "% of people working from home, 2011",
                             "employment in service, 2011 (%)", "download speed, 2011 (log) x pop. density, 2011", 
                             "download speed, 2011 (log) x population, 2011 (log)"), 
          #out=path.out, 
          single.row = FALSE, df = FALSE, omit.stat = c("rsq", "f"), 
          notes = c("Robust Std. Error parenthesis",
                    "For the GLM the Normalized diff. in ranks is used"))

@@

# path.out <- paste(path, "/outputs/table11.htm", sep = "")

stargazer(model_iv1, model_iv2, 
          type = "text", 
          se = list(rob.model_iv1[,"Std. Error"], rob.model_iv2[,"Std. Error"]), 
          dep.var.labels=c("Difference in ranks, 2011-18"),
          covariate.labels=c("download speed, 2011 (log)", "population, 2011 (log)",  
                             "broadband tests per capita, 2011", "% of unemployment, 2011", "% of British population, 2011", 
                             "population density, 2011", "% of people working from home, 2011",
                             "employment in service, 2011 (%)"),
          #out=path.out, 
          single.row = FALSE, df = FALSE, 
          omit.stat = c("rsq", "f"), notes = c("Robust Std. Error in parenthesis", "IVs: (1) Number of universities",
                                               "IVs: (2) Number of universities, Number of broadband tests, 2011"),
          add.lines = list(c(rownames(summ.fit1$diagnostics)[1],                    # use rownames as line name. in this case Weak insterumetns
                             round(summ.fit1$diagnostics[1, "statistic"], 2), 
                             round(summ.fit2$diagnostics[1, "statistic"], 2)), 
                           c(rownames(summ.fit1$diagnostics)[2], 
                             round(summ.fit1$diagnostics[2, "statistic"], 2), 
                             round(summ.fit2$diagnostics[2, "statistic"], 2)), 
                           c("P-value", 
                             round(summ.fit1$diagnostics[2, "p-value"], 2), 
                             round(summ.fit2$diagnostics[2, "p-value"], 2)), 
                           c(rownames(summ.fit1$diagnostics)[3], 
                             round(summ.fit1$diagnostics[3, "statistic"], 2), 
                             round(summ.fit2$diagnostics[3, "statistic"], 2)),
                           c("P-value", 
                             round(summ.fit1$diagnostics[3, "p-value"], 2), 
                             round(summ.fit2$diagnostics[3, "p-value"], 2))
          ))
```

### 2020-12-01 src/usa.Rmd
responses

```{r}
ggplot(data = data, aes(x=hh.net.share, y=r_diff_tr)) + geom_point() + geom_smooth(method = "lm")
```

@@

summary(base <- lm(r_diff_tr ~ hh.net.share + log(pop2013) + un13 + white2013share +
                     log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013, data = data))

@@

summary(int_density <- lm(r_diff_tr ~ hh.net.share*I(pop2013/area_h) + log(pop2013) + un13 + white2013share +
                     log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013, data = data))

@@

summary(int_pop <- lm(r_diff_tr ~ hh.net.share*log(pop2013) + log(pop2013) + un13 + white2013share +
                     log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013, data = data))

@@

summary(model_iv1 <- ivreg(r_diff_tr ~ hh.net.share + log(pop2013) + un13 + white2013share +
                     log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013 |
                       log(pop2013) + un13 + white2013share +
                       log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013 +
                       bachelors2005, data = data))
summary(model_iv1, vcov = sandwich, diagnostics = TRUE)

@@

summary(model_iv2 <- ivreg(r_diff_tr ~ hh.net.share + log(pop2013) + un13 + white2013share +
                     log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013 |
                       log(pop2013) + un13 + white2013share +
                       log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013 +
                       bachelors2005 + commuting.minutes2005, data = data))
summary(model_iv2, vcov = sandwich, diagnostics = TRUE)
```

## Table of Descriptives and Regression tables
```{r}
# Table 6
data.for.decr <- data %>%
  dplyr::select(r_diff_tr, hh.net.share, pop2013, un13,white2013share, 
                income2013, area_h, service2013, commuting.minutes2013,
                bachelors2005, commuting.minutes2005) %>%
  mutate(density = pop2013/area_h) %>%
  relocate(density, .before = service2013) %>%
  dplyr::select(-area_h)

@@

stargazer(as.data.frame(data.for.decr), out=path.out, type="html", summary = T,
          covariate.labels=c("normalized difference in ranks, 2013-18", 
                             "households w. internet, 2013 (%)", 
                             "population, 2013",  
                             "% of unemployment, 2013", 
                             "% of white population, 2013", 
                             "income, 2013",
                             "population density, 2013", 
                             "employment in service, 2011 (%)", 
                             "commute in minutes, 2013",
                             "pop. >= 25 w. Bachelor's degree, 2005 (%)",
                             "commute in minutes, 2005"))

@@

path.out <- paste(path, "/outputs/table7.htm", sep = "")

stargazer(base, int_density, int_pop, base_glm, type="html",
          se = list(rob.base[,"Std. Error"], rob.int_density[,"Std. Error"], rob.int_pop[,"Std. Error"], rob.base_glm[, "Std. Error"]), 
          dep.var.labels=c("Normalized difference in ranks 2013-18"),
          covariate.labels=c("households w. internet, 2013 (%)", 
                             "population, 2013",  
                             "% of unemployment, 2013", 
                             "% of white population, 2013", 
                             "income, 2013 (log)",
                             "population density, 2013", 
                             "employment in service, 2011 (%)", 
                             "commute in minutes, 2013", 
                             "households w. internet, 2013 (%) x pop. density, 2013", 
                             "households w. internet, 2013 (%) x population, 2013"), 
          out=path.out, single.row = FALSE, df = FALSE, 
          omit.stat = c("rsq", "f"), notes = "Robust Std. Error in parenthesis")

@@

stargazer(model_iv1, model_iv2, type = "html", 
          se = list(rob.model_iv1[,"Std. Error"], rob.model_iv2[,"Std. Error"]), 
          dep.var.labels=c("Normalized difference in ranks, 2013-18"),
          covariate.labels=c("households w. internet, 2013 (%)", 
                             "population, 2013",  
                             "% of unemployment, 2013", 
                             "% of white population, 2013", 
                             "income, 2013 (log)",
                             "population density, 2013", 
                             "employment in service, 2011 (%)", 
                             "commute in minutes, 2013"), 
          out=path.out, single.row = FALSE, df = FALSE, 
          omit.stat = c("rsq", "f"), notes = c("Robust Std. Error in parenthesis", 
                                               "IVs: (1) Bachelors degree per hab. in 2005",
                                               "IVs: (2) Bachelors degree per hab. in 2005, Commute, minutes, 2005"),
          add.lines = list(c(rownames(summ.fit1$diagnostics)[1],                    # use rownames as line name. in this case Weak insterumetns
                             round(summ.fit1$diagnostics[1, "statistic"], 2), 
                             round(summ.fit2$diagnostics[1, "statistic"], 2)), 
                           c(rownames(summ.fit1$diagnostics)[2], 
                             round(summ.fit1$diagnostics[2, "statistic"], 2), 
                             round(summ.fit2$diagnostics[2, "statistic"], 2)), 
                           c("P-value", 
                             round(summ.fit1$diagnostics[2, "p-value"], 2), 
                             round(summ.fit2$diagnostics[2, "p-value"], 2)), 
                           c(rownames(summ.fit1$diagnostics)[3], 
                             round(summ.fit1$diagnostics[3, "statistic"], 2), 
                             round(summ.fit2$diagnostics[3, "statistic"], 2)),
                           c("P-value", 
                             round(summ.fit1$diagnostics[3, "p-value"], 2), 
                             round(summ.fit2$diagnostics[3, "p-value"], 2))
          ))

>>>>

```{r}
ggplot(data = data, aes(x=hh.net.share, y=r_diff)) + geom_point() + geom_smooth(method = "lm")
```

@@

summary(base <- lm(r_diff ~ hh.net.share + log(pop2013) + un13 + white2013share +
                     log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013, data = data))

@@

summary(int_density <- lm(r_diff ~ hh.net.share*I(pop2013/area_h) + log(pop2013) + un13 + white2013share +
                     log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013, data = data))

@@

summary(int_pop <- lm(r_diff ~ hh.net.share*log(pop2013) + log(pop2013) + un13 + white2013share +
                     log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013, data = data))

@@

summary(model_iv1 <- ivreg(r_diff ~ hh.net.share + log(pop2013) + un13 + white2013share +
                     log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013 |
                       log(pop2013) + un13 + white2013share +
                       log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013 +
                       bachelors2005, data = data))
summary(model_iv1, vcov = sandwich, diagnostics = TRUE)

@@

summary(model_iv2 <- ivreg(r_diff ~ hh.net.share + log(pop2013) + un13 + white2013share +
                     log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013 |
                       log(pop2013) + un13 + white2013share +
                       log(income2013) + I(pop2013/area_h) + service2013 + commuting.minutes2013 +
                       bachelors2005 + commuting.minutes2005, data = data))
summary(model_iv2, vcov = sandwich, diagnostics = TRUE)
```

## Table of Descriptives and Regression tables
```{r}
# Table 6
data.for.decr <- data %>%
  dplyr::select(r_diff, hh.net.share, pop2013, un13,white2013share, 
                income2013, area_h, service2013, commuting.minutes2013,
                bachelors2005, commuting.minutes2005) %>%
  mutate(density = pop2013/area_h) %>%
  relocate(density, .before = service2013) %>%
  dplyr::select(-area_h)

@@

stargazer(as.data.frame(data.for.decr), out=path.out, type="html", summary = T,
          covariate.labels=c("difference in ranks, 2013-18", 
                             "households w. internet, 2013 (%)", 
                             "population, 2013",  
                             "% of unemployment, 2013", 
                             "% of white population, 2013", 
                             "income, 2013",
                             "population density, 2013", 
                             "employment in service, 2011 (%)", 
                             "commute in minutes, 2013",
                             "pop. >= 25 w. Bachelor's degree, 2005 (%)",
                             "commute in minutes, 2005"))

@@

#path.out <- paste(path, "/outputs/table7.htm", sep = "")

stargazer(base, int_density, int_pop, base_glm, 
          type="text",
          se = list(rob.base[,"Std. Error"], rob.int_density[,"Std. Error"], rob.int_pop[,"Std. Error"], rob.base_glm[, "Std. Error"]), 
          dep.var.labels=c("Difference in ranks 2013-18"),
          covariate.labels=c("households w. internet, 2013 (%)", 
                             "population, 2013",  
                             "% of unemployment, 2013", 
                             "% of white population, 2013", 
                             "income, 2013 (log)",
                             "population density, 2013", 
                             "employment in service, 2011 (%)", 
                             "commute in minutes, 2013", 
                             "households w. internet, 2013 (%) x pop. density, 2013", 
                             "households w. internet, 2013 (%) x population, 2013"), 
          #out=path.out, 
          single.row = FALSE, df = FALSE, 
          omit.stat = c("rsq", "f"), 
          notes = c("Robust Std. Error in parenthesis",
                    "For the GLM the Normalized diff. in ranks is used"))

@@

stargazer(model_iv1, model_iv2, 
          type = "text", 
          se = list(rob.model_iv1[,"Std. Error"], rob.model_iv2[,"Std. Error"]), 
          dep.var.labels=c("Difference in ranks, 2013-18"),
          covariate.labels=c("households w. internet, 2013 (%)", 
                             "population, 2013",  
                             "% of unemployment, 2013", 
                             "% of white population, 2013", 
                             "income, 2013 (log)",
                             "population density, 2013", 
                             "employment in service, 2011 (%)", 
                             "commute in minutes, 2013"), 
          #out=path.out, 
          single.row = FALSE, df = FALSE, 
          omit.stat = c("rsq", "f"), notes = c("Robust Std. Error in parenthesis", 
                                               "IVs: (1) Bachelors degree per hab. in 2005",
                                               "IVs: (2) Bachelors degree per hab. in 2005, Commute, minutes, 2005"),
          add.lines = list(c(rownames(summ.fit1$diagnostics)[1],                    # use rownames as line name. in this case Weak insterumetns
                             round(summ.fit1$diagnostics[1, "statistic"], 2), 
                             round(summ.fit2$diagnostics[1, "statistic"], 2)), 
                           c(rownames(summ.fit1$diagnostics)[2], 
                             round(summ.fit1$diagnostics[2, "statistic"], 2), 
                             round(summ.fit2$diagnostics[2, "statistic"], 2)), 
                           c("P-value", 
                             round(summ.fit1$diagnostics[2, "p-value"], 2), 
                             round(summ.fit2$diagnostics[2, "p-value"], 2)), 
                           c(rownames(summ.fit1$diagnostics)[3], 
                             round(summ.fit1$diagnostics[3, "statistic"], 2), 
                             round(summ.fit2$diagnostics[3, "statistic"], 2)),
                           c("P-value", 
                             round(summ.fit1$diagnostics[3, "p-value"], 2), 
                             round(summ.fit2$diagnostics[3, "p-value"], 2))
          ))
